\section {Conventions}
This section of this document describes some conventions the document will
adhere to from now on.

\paragraph{Constant Value Convention}
Constant values in this document are referred to via names for easy of 
readabilty. They are represented as teal colored capital words with underscores
(\_) as word separators. For example \constant{MAGIC\_WORD} is a well defined
constant in this document.
All refered constants are documented in this document at the section 
``Constants''. Please refer to this section for their descriptions and their 
values. If a constant reference has an asterisk (*), this means any constant
that starts with the expression to the left of the asterisk, or ends with the
expression to the right of the asterisk. For example \constant{TYPE\_*} refers
to all constants of the ``node type'' constant group.

\paragraph{Primitive Size Convention}
The primitive sizes this document follow the convention of the C\# language 
conventions. Please refer to the section ``Definitions'' for their exact 
definition. Some examples following other languages' conventions are also
given. They are represented as lowercase blue words. For example \keyword{byte}
is an unsigned 1-byte wide integer type.

\paragraph{Number Base Representation Convention}
This document follows number base representation conventions of the C family of
languages. Expressions starting with \hex{} are numbers in base-16, otherwise
they are in base-10. Octal bases are never used in this document.

\paragraph{Requisite Convention}
Throughout this document some words like \must, \should, and \may have reserved
meanings when formatted as given. Please refer to the section ``Definitions'' 
for their reserved meanings. 